The User Behavior On Online Judge Website

### 2017-05-13 paper.tex
complete class paper

\title{The User Behavior On Online Judge Website}
\author{yueyi zhuo}
%\institute{School of Mathematical,Sichuan Normal University}
\date{2017}

@@

Abstract content.

@@

\section{The time series view}

@@

@@

If a solver encounter a hard problem that he can't solve, he may drop the website or wait to time that he can
solve it, that is what above model want to match. But we can consider another behavior in which solver will
try to skip the problem and to solve the next one. If the hard problem is \textit{isolated}, we can expect
the decrease shock caused by the problem will be compressd. For match this, I specify the 2 lag item:

@@

So we can confirm that it is true that solver try to solve latter problem has more steady belief.
The dummy variable method can't be used futher since the condition number has implies the rise of multicolinearity.

@@

I have build a more realistic probility model and fail to extend it as you see. 
Then I develope a indirect time series like model to verify some hypothesis. I can draw conclusion from these survey:

1. Difficulty shock exists significance but it has not memory 
2. The boru solver seems stable more than raw solver when they encounter hard problem.

>>>>

\title{The User Behavior On Online Judge Website}
\author{yueyi zhuo (2014060843)}
%\institute{School of Mathematical,Sichuan Normal University}
\date{2017}

@@

In this paper, I develope two types of model to investigate Online Judge website solve record 
and verify some factor holded by order, solver and problem difficulty structure.

@@

\section{The time series like model}

@@

The fitting figure is:

\includegraphics[scale=0.55]{tail2.png}

@@

If a solver encounter a hard problem that he can't solve, he may drop the website or wait to time that he can
solve it, that is what above model want to match. But we can consider another behavior in which solver will
try to skip the problem and to solve the next one. If the hard problem is \textit{isolated}, we can expect
the decrease shock caused by the problem will be compressd. For match this, I try to specify the more lag item:

@@

So we can confirm that it is true that solver try to solve latter problem has more steady belief.
The dummy variable method can't be used futher since the condition number has implies the rise of multicolinearity,
thus we get a unsignicant result. But if I replace dummy variable $hard$ to original fake quantity $diff$ variable,
replace $right$ to original order variable $id$, we can get a signicant result:

\[
solve_i = \beta_1 solve_{i-1} + \beta_2 solve_{i-2} + \beta_3 solve_{i-3} + \beta_4 diff \, solve_{i-1} +
		  \beta_5 diff \, id \, solve_{i-1} + \epsilon_i
\]

\begin{center}
\begin{tabular}{lclc}
\toprule
\textbf{Dep. Variable:}    &      solve       & \textbf{  R-squared:         } &     0.970   \\
\textbf{Model:}            &       OLS        & \textbf{  Adj. R-squared:    } &     0.969   \\
\textbf{Method:}           &  Least Squares   & \textbf{  F-statistic:       } &     1619.   \\
\textbf{Date:}             & Sat, 13 May 2017 & \textbf{  Prob (F-statistic):} & 2.34e-190   \\
\textbf{Time:}             &     14:47:52     & \textbf{  Log-Likelihood:    } &   -2737.6   \\
\textbf{No. Observations:} &         259      & \textbf{  AIC:               } &     5485.   \\
\textbf{Df Residuals:}     &         254      & \textbf{  BIC:               } &     5503.   \\
\textbf{Df Model:}         &           5      & \textbf{                     } &             \\
\bottomrule
\end{tabular}
\begin{tabular}{lccccc}
                          & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
\midrule
\textbf{solve\_l1}         &       0.7618  &        0.068     &    11.162  &         0.000        &         0.627     0.896       \\
\textbf{solve\_l2}         &       0.1196  &        0.062     &     1.931  &         0.055        &        -0.002     0.242       \\
\textbf{solve\_l3}         &       0.1470  &        0.045     &     3.245  &         0.001        &         0.058     0.236       \\
\textbf{solve\_l1:diff}    &      -0.0302  &        0.008     &    -3.921  &         0.000        &        -0.045    -0.015       \\
\textbf{solve\_l1:diff:id} &       0.0001  &     5.47e-05     &     2.705  &         0.007        &      4.02e-05     0.000       \\
\bottomrule
\end{tabular}
\begin{tabular}{lclc}
\textbf{Omnibus:}       & 98.904 & \textbf{  Durbin-Watson:     } &     2.245  \\
\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &  1333.652  \\
\textbf{Skew:}          &  1.107 & \textbf{  Prob(JB):          } & 2.52e-290  \\
\textbf{Kurtosis:}      & 13.894 & \textbf{  Cond. No.          } &  4.16e+03  \\
\bottomrule
\end{tabular}
%\caption{OLS Regression Results}
\end{center}

This imply a continual decline of effect of difficulty shock.

@@

I have built a more realistic probility model and fail to extend it as you see. 
Then I develope a indirect time series like model to verify some hypothesis. I can draw conclusion from these survey:

1. Difficulty shock exists significance but it has not memory

2. The boru solver seems stable more than raw solver when they encounter hard problem.

From result, I can point out that OJ website should place their difficulty problem into proper(latter)
 location to match solver structure to maximize their business and activity.
